---
title: rmd_post_test
author: Kasia
date: '2020-11-18'
slug: []
categories: []
tags: []
description: 'jskskjdkjs'
featured: ''
featuredalt: ''
featuredpath: ''
linktitle: ''
type: post
---




## 1. Set up a Github repository

## 2. Install Hugo

## 3. Post from RStudio using RMarkdown

Let's add a table, just for kicks.

| hours of sun | happiness |
|---|---|
| 0 | 1 |
| 3 | 4 |
| 5 | 7 |
| 7 | 10 |


```{r eval=TRUE}
library(ggplot2)
mean(iris$Sepal.Length)
require(ggplot2)
ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  scale_color_manual(values = c("#3B9AB2", "#E4B80E", "#F21A00"))

```

```{r}
library(dygraphs)
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>% dyRangeSelector()

```

## Intro

This post is the result of my journey with setting up the page by using:
Hugo: for the template
Github Pages: for hosting.

What was important for me, I also wanted to post my RMarkdown files, as I am R-lady. I went through many pages with the guidelines and in this post I will show you, how to make it happen!
